From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-06 article/article.tex
Handling plot of figures
Added notebook for dblp

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{color}
\usepackage{authblk}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
%PREPRINT/MANUSCRIPT OPTIONS
\usepackage{setspace}
\usepackage{lineno}
\linenumbers
\doublespacing
\DeclareMathOperator*{\argmax}{argmax}
%opening

% \author{
%     \IEEEauthorblockN{James Gilbert\IEEEauthorrefmark{1}, Nicole Pearcy\IEEEauthorrefmark{1}, Jamie Twycross\IEEEauthorrefmark{2}}
%     \IEEEauthorblockA{\IEEEauthorrefmark{1}Synthetic Biology Research Centre, School of Life Sciences, University of Nottingham}
%     \IEEEauthorblockA{\IEEEauthorrefmark{2}Intelligent Modelling and Analysis Group, School of Computer Science, University of Nottingham}
% }

@@

\title{From clusters to queries: exploiting uncertainty in the modular landscape of complex networks}

%\titlerunning{Short form of title}        % if too long for running head

\author{James P Gilbert         \and
	Jamie Twycross 		\and
	John King
	}
\date{Received: date / Accepted: date}

@@

\begin{figure}
\centering
 \includegraphics[width=0.7\textwidth]{images/search_space_3.png}
 \caption{
 Modularity search space of the \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region. 
  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.
 }
 \label{fig:modular_search_space}
\end{figure}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
        \caption{1000 nodes}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
     Error bars represent standard deviations.}
\end{figure*}

@@

\begin{figure}[ht]
     \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
        \caption{EU email departments}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
        \caption{Yeast PPI protein complexes}
    \end{subfigure}

    \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Communities are ordered by size.
    Error bars indicate standard deviation.
    }
    \label{fig:real_network_results}
\end{figure}

\begin{figure}[ht]
     \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
        \caption{EU email departments (986 nodes)}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
        \caption{Yeast PPI protein complexes (1628 nodes)}
    \end{subfigure}

    \caption{Receiver Operator Characteristic curves for node communities.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Represents mean, shaded area indicates standard deviation.
    }
    \label{fig:real_network_nodwise_classifiers}
\end{figure}

>>>>

\listfiles
\documentclass[manuscript, review, sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{color}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}

\usepackage{booktabs} 
\DeclareMathOperator*{\argmax}{argmax}

\date{Received: date / Accepted: date}

@@

\title{From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks}

\author{James P Gilbert}
\affiliation{%
  \institution{Synthetic biology research centre}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{james.gilbert@nottingham.ac.uk}

\author{Jamie Twycross}
\affiliation{%
  \institution{School of Computer Science}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{jamie.twycross@nottingham.ac.uk}

\author{John King}
\affiliation{%
  \institution{School of Mathematical Sciences}
  \streetaddress{University of Nottingham}
  \city{Nottingham}
  \country{United Kingdom}
  \postcode{NG7 2RD}
}
\email{john.king@nottingham.ac.uk}

@@

\begin{figure}
\centering
 \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
 \caption{
 Modularity search space of the \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region. 
  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.
 }
 \label{fig:modular_search_space}
\end{figure}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_5000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
     Error bars represent standard deviations.}
\end{figure*}

@@

\begin{figure*}
     \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
        \caption{EU email departments}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
        \caption{Yeast PPI protein complexes}
    \end{subfigure}
    \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Communities are ordered by size.
    Error bars indicate standard deviation.
    }
    \label{fig:real_network_results}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
        \caption{EU email departments (986 nodes)}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
        \caption{Yeast PPI protein complexes (1628 nodes)}
    \end{subfigure}
    \caption{Receiver Operator Characteristic curves for node communities.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Represents mean, shaded area indicates standard deviation.
    }
    \label{fig:real_network_nodwise_classifiers}
\end{figure*}
